---
title: "Mean MaxN Comparison"
author: "Jessica Madden"
date: "December 16, 2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(wesanderson)
```

```{r}
# Read in point data

point_data_complete <- read_csv(here("data", "point_data_complete.csv"))
five_min <- read_csv(here("data", "point_data_fivemin_complete.csv"))
ten_min <- read_csv(here("data", "point_data_tenmin_complete.csv"))
```
# Mean MaxN through time
### Barred surfperch at Percos and Refugio

```{r}
# Case study: Percos vs Refugio comparison of mean MaxN of barred surfperch
# Get mean maxN for each 5 min interval

perc_ref_five <- five_min %>% 
  filter(site_full %in% c("Percos", "Refugio")) %>%
  filter(common == "Barred surfperch") 

perc_ref_five_summary <- perc_ref_five %>% 
  group_by(op_code, site_full, common, five_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(five_min, site_full) %>% 
  summarize(
    mean_maxn = mean(maxn), 
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  ) 

# Get mean maxN for each 10 min interval

perc_ref_ten <- ten_min %>% 
  filter(site_full %in% c("Percos", "Refugio")) %>%
  filter(common == "Barred surfperch") 

perc_ref_ten_summary <- perc_ref_ten %>% 
  group_by(op_code, site_full, common, ten_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(ten_min, site_full) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )
```


```{r, fig.align='center', fig.width=10}
ggplot(perc_ref_ten_summary, aes(x = ten_min, y = mean_maxn, fill = site_full)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = ten_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_x_continuous(limits = c(0, 65), 
                     n.breaks = 6) +
  scale_y_continuous(limits = c(0, 11.5), 
                     n.breaks = 10) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Barred surfperch Mean MaxN", subtitle = "Averaged across deployments for each 10 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("barred_5min.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(perc_ref_five_summary, aes(x = five_min, y = mean_maxn, fill = site_full)) +
  geom_bar(stat="identity", 
           position = "dodge") +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = five_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 5)) +
  scale_x_continuous(limits = c(0, 66), 
                     n.breaks = 11) +
  scale_y_continuous(limits = c(0, 12), 
                     n.breaks = 10) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Barred surfperch Mean MaxN", subtitle = "Averaged across deployments for each 5 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("barred_10min.png", width = 10, height = 5)
```


### Leopard sharks at Dume Cove and Leo Carrillo
```{r}
# Case study: Dume vs Leo comparison of mean MaxN of leopard sharks
# Get mean maxN for each 5 min interval

dume_leo_five <- five_min %>% 
  filter(site_full %in% c("Dume Cove", "Leo Carrillo")) %>%
  filter(common == "Leopard shark") %>% 
  group_by(op_code, site_full, common, five_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(five_min, site_full) %>% 
  summarize(
    mean_maxn = mean(maxn), 
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )

# Get mean maxN for each 10 min interval

dume_leo_ten <- ten_min %>% 
  filter(site_full %in% c("Dume Cove", "Leo Carrillo")) %>%
  filter(common == "Leopard shark") %>% 
  group_by(op_code, site_full, common, ten_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(ten_min, site_full) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )
```


```{r, fig.align='center', fig.width=10}
ggplot(dume_leo_ten, aes(x = ten_min, y = mean_maxn, fill = site_full)) +
  geom_bar(stat="identity", 
           position = "dodge") +  
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = ten_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_x_continuous(limits = c(0, 65), 
                     n.breaks = 6) +
  scale_y_continuous(limits = c(0, 1),
                     n.breaks = 4) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Leopard shark Mean MaxN", subtitle = "Averaged across deployments for each 10 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("leopard_10min.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(dume_leo_five, aes(x = five_min, y = mean_maxn, fill = site_full)) +
  geom_bar(stat="identity", 
           position = "dodge") +  
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = five_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 5)) +
  scale_x_continuous(limits = c(0, 65), 
                     n.breaks = 11) +
  scale_y_continuous(limits = c(0, 1), 
                     n.breaks = 4) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Leopard shark Mean MaxN", subtitle = "Averaged across deployments for each 5 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("leopard_5min.png", width = 10, height = 5)
```

### Unknown silversides at South Campus and Haskells

```{r}
# Case study: South Campus vs Haskells comparison of mean MaxN of unknown Atherinid
# Get mean maxN for each 5 min interval

soca_habe_five <- five_min %>% 
  filter(site_full %in% c("South Campus", "Haskells")) %>%
  filter(common == "Unknown Silverside") 

soca_habe_five_summary <- soca_habe_five %>% 
  group_by(op_code, site_full, geog, common, five_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(five_min, site_full, geog) %>% 
  summarize(
    mean_maxn = mean(maxn), 
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  ) %>% 
  arrange(geog, five_min)

# Get mean maxN for each 10 min interval

soca_habe_ten <- ten_min %>% 
  filter(site_full %in% c("South Campus", "Haskells")) %>%
  filter(common == "Unknown Silverside") 

soca_habe_ten_summary <- soca_habe_ten %>% 
  group_by(op_code, site_full, geog, common, ten_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(ten_min, site_full, geog) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  ) %>% 
  arrange(geog, ten_min)
```


```{r, fig.align='center', fig.width=10}
ggplot(soca_habe_ten_summary, aes(x = ten_min, y = mean_maxn, fill = reorder(site_full, geog))) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = ten_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_x_continuous(n.breaks = 6) +
  scale_y_continuous(limits = c(0, 9), 
                     n.breaks = 9) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Unknown silverside Mean MaxN", subtitle = "Averaged across deployments for each 10 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("silverside_10min.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(soca_habe_five_summary, aes(x = five_min, y = mean_maxn, fill = reorder(site_full, geog))) +
  geom_bar(stat="identity", 
           position = "dodge") +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = five_min, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = 2, 
                alpha = 0.9, 
                position = position_dodge(width = 5)) +
  scale_x_continuous(n.breaks = 11, 
                     limits = c(0, 64)) +
  scale_y_continuous(limits = c(0, 9), 
                     n.breaks = 9) +
  labs(x = "Time (minutes)", y = "Mean MaxN (+/- SE)", title = "Unknown silverside Mean MaxN", subtitle = "Averaged across deployments for each 5 min segment of 60 min videos") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  ggsave("silverside_5min.png", width = 10, height = 5)
```

# Mean MaxN across sites

Mean Max N comparison between: 

-  deployments as replicates 
-  5 min time segments as replicates 
-  10 min time segments as replicates for each site

### Barred surfperch at all sites

```{r}
# Total MaxN

barred <- point_data_complete %>% 
  filter(common == "Barred surfperch") %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    maxn = max(number)
  ) %>% 
  arrange(geog)

# Each deployment as replicate for each site

barred_all <- point_data_complete %>% 
  filter(common == "Barred surfperch") %>% 
  group_by(op_code, site_full, type, geog, date, bruv, subclass, family, common) %>% 
  summarize(
    maxn = max(number)
  ) %>%
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn), 
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  ) %>% 
  arrange(geog)

# Each 10 min time segment as replicate for each site

barred_ten <- ten_min %>% 
  filter(common == "Barred surfperch") %>% 
  group_by(op_code, site_full, type, geog, common, ten_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )

# Each 5 min time segment as replicate for each site

barred_five <- five_min %>% 
  filter(common == "Barred surfperch") %>% 
  group_by(op_code, site_full, type, geog, common, five_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )

```

```{r, fig.align='center', fig.width=10}
ggplot(barred, aes(x = reorder(site_full, -geog), y = maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  scale_y_continuous(n.breaks = 10) +
  labs(x = "Site", y = "MaxN", title = "Barred surfperch MaxN", subtitle = "Not an average") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("barred_sites.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(barred_all, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Barred surfperch Mean MaxN", subtitle = "Averaged with each deployment as replicate") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("barred_sites_dep.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(barred_ten, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(limits = c(0, 9), 
                     n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Barred surfperch Mean MaxN", subtitle = "Averaged across each 10 minute segment of 60 min deployment") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("barred_sites_10min.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(barred_five, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(limits = c(0, 9),
                     n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Barred surfperch Mean MaxN", subtitle = "Averaged across each 5 minute segment of 60 min deployment") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("barred_sites_5min.png", width = 10, height = 5)
```

#### Yellowfin croaker at all sites

```{r}
# Each deployment as replicate for each site

yf <- point_data_complete %>% 
  filter(common == "Yellowfin croaker") %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    maxn = max(number)
  ) %>%
  arrange(geog)

# Each deployment as replicate for each site

yf_all <- point_data_complete %>% 
  filter(common == "Yellowfin croaker") %>% 
  group_by(op_code, site_full, type, geog, date, bruv, subclass, family, common) %>% 
  summarize(
    maxn = max(number)
  ) %>%
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn), 
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  ) %>% 
  arrange(geog)

# Each 10 min time segment as replicate for each site

yf_ten <- ten_min %>% 
  filter(common == "Yellowfin croaker") %>% 
  group_by(op_code, site_full, type, geog, common, ten_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )

# Each 5 min time segment as replicate for each site

yf_five <- five_min %>% 
  filter(common == "Yellowfin croaker") %>% 
  group_by(op_code, site_full, type, geog, common, five_min) %>% 
  summarise(
    maxn = max(number)
  ) %>% 
  group_by(site_full, type, geog) %>% 
  summarize(
    mean_maxn = mean(maxn),
    sd = sd(maxn), 
    se = sd(maxn)/(sqrt(n())),
    sample_size = n()
  )

```

```{r, fig.align='center', fig.width=10}
ggplot(yf, aes(x = reorder(site_full, -geog), y = maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  scale_y_continuous(n.breaks = 10) +
  labs(x = "Site", y = "MaxN", title = "Yellowfin croaker MaxN", subtitle = "Not an average") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("yf_sites.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(yf_all, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Yellowfin croaker Mean MaxN", subtitle = "Averaged with each deployment as replicate") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("yf_sites_dep.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(yf_ten, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(limits = c(0, 7),
                     n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Yellowfin croaker Mean MaxN", subtitle = "Averaged across each 10 minute segment of 60 min deployment") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("yf_sites_10min.png", width = 10, height = 5)
```

```{r, fig.align='center', fig.width=10}
ggplot(yf_five, aes(x = reorder(site_full, -geog), y = mean_maxn, fill = type)) +
  geom_bar(stat="identity", 
           position = "dodge")  +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  geom_errorbar(aes(x = site_full, ymax = mean_maxn + se, ymin = mean_maxn - se), 
                width = .2, 
                alpha = 0.9, 
                position = position_dodge(width = 10)) +
  scale_y_continuous(limits = c(0, 7),
                     n.breaks = 10) +
  labs(x = "Site", y = "Mean MaxN (+/- SE)", title = "Yellowfin croaker Mean MaxN", subtitle = "Averaged across each 5 minute segment of 60 min deployment") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  coord_flip() +
  ggsave("yf_sites_5min.png", width = 10, height = 5)
```