---
title: "BRUV data summary 2019"
author: "Jessica Madden"
date: "November 30, 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(here)
library(tidyverse)
library(kableExtra)
library(janitor)
library(data.table)
library(knitr)

# Load in data
max_n_data <- read.csv(here("data", "max_n_data.csv")) %>% 
  clean_names()
```


```{r}
# Count number of distinct species

species_total <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  pull(sp_code) %>% 
  n_distinct()

# Count number of distinct families

families_total <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  pull(family_x) %>% 
  n_distinct()
```


A total of **`r species_total` species** belonging to **`r families_total` families** were recorded from BRUV deployments at all of the locations combined. This summary includes MaxN data recorded to species (with the exception of the category 'unknown silversides'). There are a number of point tags that are to genus, family, or unknown that are not included here, though these tags that are excluded should not greatly affect the species richness or MaxN data represented here.


```{r}
# Calculate number of deployments in which each species is present for each site

presence <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(site_full) %>% 
  count(sp_code, common) %>% 
  rename("count" = "n")
  
#Calculate number of deployments for each site from max_n_data data frame

number_deployments <- max_n_data %>% 
  group_by(site_full) %>% 
  summarize(deployments = n_distinct(op_code))

# Join data frames and calc % presence for each species site combination

presence_table <- presence %>% 
  full_join(number_deployments, by = "site_full") %>% 
  mutate(deployments = as.numeric(deployments)) %>% 
  mutate(perc_presence = (count / deployments)*100)

# Obtain Max % presence for each species

max_presence_table <- presence_table %>% 
  group_by(common) %>% 
  summarize(max_presence = max(perc_presence))
```


### Species Richness

```{r}
sp_richness <- max_n_data %>% 
 filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(site_full, geog, type) %>% 
  summarise(n_distinct(common)) %>% 
  rename("sp_richness" = "n_distinct(common)") %>% 
  arrange(geog) %>% 
  cbind(pair = c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5)) %>% 
  arrange(geog)
```

***Table 1.** Total species richness at each site. Species richness represents number of unique species (Actinopterygii, Elasmobranchii) observed in all BRUV videos at each site (n = 9). For all MPA/Reference pairs except the San Diego site, the MPA site had greater species richness.*
```{r}
richness_table <- sp_richness %>% 
  rename("Species richness" = "sp_richness") %>% 
  rename("Type" = "type") %>% 
  rename("Site" = "site_full") %>% 
  subset(select= c(-geog, -pair)) %>% 
  kbl() %>% 
  kable_styling()
richness_table
```

```{r}
ggplot(sp_richness, aes(x = pair, y = sp_richness, fill = site_full)) +
  geom_bar(stat = "identity", 
           position = "dodge", 
           aes(fill = type)) +
  coord_flip() +
  labs(x = "Site", y = "Total species richness") +
  theme_minimal() +
  guides(fill=guide_legend(title="Type"))
```

***Figure 1.** Total species richness at each site. Species richness represents number of unique species (Actinopterygii, Elasmobranchii) observed in all BRUV videos at each site (n = 9). Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude.*

### Mean species richness: MPA vs. Reference comparison

Average number of unique individuals of either subclass Actinopterygii or Elasmobranchii per bruv deployment in MPAs vs. Reference sites

```{r}
mpa_ref_mean_richness <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(op_code, type) %>% 
  summarise(n_distinct(common)) %>% 
  rename("sp_rich" = "n_distinct(common)") %>% 
  group_by(type) %>% 
  summarise(
    mean_richness = mean(sp_rich), 
    sd_richness = sd(sp_rich),
    min = min(sp_rich), 
    max = max(sp_rich),
    sample_size = n()
  ) %>% 
  mutate(standard_error = sd_richness/(sqrt(sample_size)))
  
# Plot it

ggplot(mpa_ref_mean_richness, aes(x = type, y = mean_richness)) +
  geom_bar(stat = "identity", 
           aes(fill = type),
           color="black", 
           size=0.25) +
  geom_errorbar(aes(x = type, ymax = mean_richness + standard_error, ymin = mean_richness - standard_error), 
                width = 0.05, 
                alpha = 0.9) +
  labs(y = "Mean species richness", x = "", title = "Mean species richness by MPA status") +
  theme(axis.line.x = element_line(size=0.25),
                     axis.line.y = element_line(size=0.25),
                     axis.text.x = element_text(size=8, color="black", vjust=0.3),
                     axis.text.y = element_text(size=8, color="black"),
                     axis.ticks=element_line(color="black", size=0.25),
                     axis.title.x = element_text(size = 10, color = "black"),
                     legend.position="none",
                     panel.background=element_blank(),
                     panel.grid=element_blank(),
                     plot.title=element_text(face="italic", hjust=0.5),
                     strip.background=element_blank(),
                     strip.text=element_text(size=8))
```

***Figure.** Mean species richness with MPA and reference sites, averaged from each BRUV deployment.*

### Mean Total Species Richness

```{r}
mean_richness <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(site_full, family_x, sp_code, common) %>% 
  group_by(site_full, date, bruv, geog, type) %>% 
  summarise(n_distinct(common)) %>% 
  rename("sp_rich" = "n_distinct(common)")

mean_richness_table <- mean_richness %>% 
  group_by(site_full, geog, type) %>% 
  summarise(mean_sp_richness = mean(sp_rich), 
            sd_sp_richness = sd(sp_rich), 
            min_sp_richness = min(sp_rich), 
            max_sp_richness = max(sp_rich), 
            median_sp_richness = median(sp_rich), 
            n_sp_richness = n()) %>% 
  mutate(standard_error = (sd_sp_richness / sqrt(n_sp_richness))) %>% 
  arrange(geog)
```
***Table 2.** Summary statistics of species richness from BRUV deployments at ten sampling locations. Mean species richness represents the number of unique species (Actinopterygii, Elasmobranchii) observed in each deployment averaged across all deployments for each site.*
```{r}
mean_richness_table_clean <- mean_richness_table %>%  
  select("site_full", "type", "mean_sp_richness", "standard_error", "min_sp_richness", "max_sp_richness", "n_sp_richness") %>% 
  subset(select = (-geog)) %>% 
  kable(digits=2, 
        col.names = c("Site", "Type", "Mean species richness", "Standard Error", "Min", "Max", "Sample size")) %>% 
  kable_styling()
mean_richness_table_clean
```

```{r}
ggplot(mean_richness_table, aes(x = reorder(site_full, -geog), y = mean_sp_richness)) +
  geom_bar(stat = "identity", 
           aes(fill = type)) +
  geom_errorbar(aes(x = site_full, ymax = mean_sp_richness + standard_error, ymin = mean_sp_richness - standard_error), 
                width = 0.3, 
                alpha = 0.9) +
  labs(y = "Mean species richness", x = "Site", title = "Mean species richness") +
  theme_minimal() +
  coord_flip() +
  guides(fill=guide_legend(title="Type"))
```

***Figure 2.** Mean species richness at each site. Mean species richness represents the number of unique species (Actinopterygii, Elasmobranchii) observed in each deployment averaged across all deployments for each site (n = 9). Error bars indicate standard error. Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude.*


### Mean species richness: Actinopterygii

```{r}
# Add in zero values for bruvs where no fish present

mean_f_rich <- max_n_data %>% 
  filter(subclass == "Actinopterygii") %>% 
  group_by(site_full, date, bruv, geog, type) %>% 
  summarise(n_distinct(common)) %>% 
  rename("sp_rich" = "n_distinct(common)")

distinct_op_code <- max_n_data %>% 
  distinct(op_code, .keep_all = TRUE) %>% 
  select(site_full, geog, type, date, bruv)

mean_fish_richness <- mean_f_rich %>% 
  full_join(distinct_op_code, by = c("site_full", "geog", "type", "date", "bruv"))
  
# Change NAs to zeroes

mean_fish_richness[is.na(mean_fish_richness)] = 0

mean_fish_richness_table <- mean_fish_richness %>% 
  group_by(site_full, geog, type) %>% 
  summarise(mean_sp_richness = mean(sp_rich), 
            sd_sp_richness = sd(sp_rich), 
            min_sp_richness = min(sp_rich), 
            max_sp_richness = max(sp_rich), 
            median_sp_richness = median(sp_rich), 
            n_sp_richness = n()) %>% 
  arrange(geog)

# Plot data

ggplot(mean_fish_richness_table, aes(x = reorder(site_full, -geog), y = mean_sp_richness)) +
  geom_bar(stat = "identity", 
           aes(fill = type)) +
  geom_errorbar(aes(x = site_full, ymax = mean_sp_richness + sd_sp_richness, ymin = mean_sp_richness - sd_sp_richness), 
                width = 0.3, 
                alpha = 0.9) +
  labs(y = "Mean species richness", x = "Site", title = "Mean fish species richness") +
  theme_minimal() +
  coord_flip() +
  guides(fill=guide_legend(title="Type"))

```

### Mean species richness: Elasmobranchii

```{r}
# Add in zero values for bruvs where no elasmos present

mean_e_rich <- max_n_data %>% 
  filter(subclass == "Elasmobranchii") %>% 
  group_by(site_full, date, bruv, geog, type) %>% 
  summarise(n_distinct(common)) %>% 
  rename("sp_rich" = "n_distinct(common)")

mean_elasmo_richness <- mean_e_rich %>% 
  full_join(distinct_op_code, by = c("site_full", "geog", "type", "date", "bruv"))
  
# Change NAs to zeroes

mean_elasmo_richness[is.na(mean_elasmo_richness)] = 0

mean_elasmo_richness_table <- mean_elasmo_richness %>% 
  group_by(site_full, geog, type) %>% 
  summarise(mean_sp_richness = mean(sp_rich), 
            sd_sp_richness = sd(sp_rich), 
            min_sp_richness = min(sp_rich), 
            max_sp_richness = max(sp_rich), 
            median_sp_richness = median(sp_rich), 
            n_sp_richness = n()) %>% 
  arrange(geog)

# Plot data

ggplot(mean_elasmo_richness_table, aes(x = reorder(site_full, -geog), y = mean_sp_richness)) +
  geom_bar(stat = "identity", 
           aes(fill = type)) +
  geom_errorbar(aes(x = site_full, ymax = mean_sp_richness + sd_sp_richness, ymin = mean_sp_richness - sd_sp_richness), 
                width = 0.3, 
                alpha = 0.9) +
  labs(y = "Mean species richness", x = "Site", title = "Mean elasmobranch species richness") +
  theme_minimal() +
  coord_flip() +
  guides(fill=guide_legend(title="Type"))
```

### MaxN 

#### MaxN by species

MaxN statistic represents the maximum number of individuals belonging to each species counted in a single frame, across all sampling videos at each site (n = 9). Max % presence is the percentage of deployments in which a species is present, from the site in which the species had the highest % presence. 

```{r}
maxN_table <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(site_full, geog, common, family_x) %>% 
  summarise(maxN = max(max_n))

# Transpose site data into columns

maxN_wider <- maxN_table %>% 
  pivot_wider(id_cols = c(common, family_x), 
              names_from = site_full, 
              values_from = maxN) %>% 
  arrange(family_x) %>% 
  full_join(max_presence_table, by = "common") %>% 
  relocate(max_presence, .after = family_x) %>%  
  relocate(Percos, .after = max_presence) %>% 
  relocate(Refugio, .after = Percos) %>% 
  relocate("South Campus", .after = Refugio) %>% 
  relocate("Dume Cove", .after = Haskells) %>% 
  relocate(Scripps, .after = Strands) %>% 
  relocate("San Elijo", .after = Scripps) %>%   
  rename("Common name" = "common", "Family" = "family_x", "Max % presence" = "max_presence")


# Change NAs to zeroes

#maxN_wider[is.na(maxN_wider)] = 0
```

***Table 3.** MaxN statistic for each species present at the 10 sampling locations and Max % presence at any one location. * 
```{r}
opts <- options(knitr.kable.NA = "")

maxN_wider %>% 
  kable(digits = 0) %>% 
  kable_styling()
```


```{r}
ggplot(maxN_table, aes(fill = common, x = reorder(site_full, -geog), y = maxN)) +
  geom_bar(position = "stack", stat = "identity") +
  coord_flip() +
  labs(x = "Site", y = "Max N") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification = "left",
        legend.title = element_blank(), 
        legend.text = element_text(size = 8))


```

***Figure 3.** MaxN statistic for each site. Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude. Stacked colors indicate unique species, with the exception of 'unknown silversides' possibly including topsmelt.*

```{r}
ggplot(maxN_table, aes(fill = common, x = reorder(site_full, -geog), y = maxN)) +
  geom_bar(position = "fill", stat = "identity") +
  coord_flip() +
  labs(x = "Site", y = "% Max N") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification = "left",
        legend.title = element_blank(), 
        legend.text = element_text(size = 8))
```

***Figure 4.** Composition of species at each site as a proportion of MaxN recorded. Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude. Stacked colors indicate unique species, with the exception of 'unknown silversides' possibly including topsmelt.*

#### Max N by family

```{r}
# Make table of maxN aggregated by family

maxN_fam_table <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>% 
  group_by(site_full, geog, common, family_x) %>% 
  summarise(sp_maxN = max(max_n)) %>%
  group_by(site_full, geog, family_x) %>% 
  summarise(fam_maxN = sum(sp_maxN))
  

ggplot(maxN_fam_table, aes(fill = family_x, x = reorder(site_full, -geog), y = fam_maxN)) +
  geom_bar(position = "stack", stat = "identity") +
  coord_flip() +
  labs(x = "Site", 
       y = "Max N") +
  theme_minimal() +
  theme(legend.position = "top", 
        legend.title = element_blank())
```

***Figure 5. ** MaxN statistic aggregated by family for each site. Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude. Stacked colors indicate unique families.*

```{r}
ggplot(maxN_fam_table, aes(fill = family_x, x = reorder(site_full, -geog), y = fam_maxN)) +
  geom_bar(position = "fill", stat = "identity") +
  coord_flip() +
  labs(x = "Site", y = "% Max N") +
  theme_minimal() +
  theme(legend.position = "top", 
        legend.title = element_blank())

```
 
***Figure 6.** Composition of species aggregated by family at each site as a proportion of MaxN recorded. Percent contribution of MAxN is between 0 - 1.0. Sites are ordered MPA first and reference second, with pairs in order of decreasing latitude. Stacked colors indicate unique families.*

```{r eval=FALSE}
ggplot(maxN_fam_table, aes(fill = site_full, x = family_x, y = fam_maxN)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(x = "Site", y = "Max N") +
  coord_flip() +
  theme_minimal()
```

### Proportion of catch

```{r, eval=FALSE}
site_proportion_data <- species_summary_by_site %>%
  group_by(site) %>%
  mutate(total_fish_caught = sum(no_fish)) %>%
  mutate(prop_of_catch = no_fish/total_fish_caught)
```



### Mean maxN


```{r}
# Change NAs to zeroes

maxN_wider[is.na(maxN_wider)] = 0

max_n_longer <- maxN_wider %>% 
  clean_names() %>% 
  pivot_longer(cols = `percos`:`san_elijo`, 
               names_to = "Site", 
               values_to = "max_n")
  
sampling_dates <- max_n_data %>% 
  select("site_full", "geog", "date", "type", "bruv") %>% 
  distinct(date, bruv, .keep_all = TRUE)

# Compile species list for each site

species_list_site <- max_n_data %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select("site_full", "geog", "type", "common", "family_x") %>%
  group_by(site_full) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  mutate(max_n = 0)

# Join species list with maxN data to get zeroes for species absent in deployments within a site where they are present
#Percos

perc_dates <- sampling_dates %>% 
  filter(site_full == "Percos") %>% 
  select(site_full, date, bruv)

perc_sp <- species_list_site %>% 
  filter(site_full == "Percos") %>% 
  merge(perc_dates, by="site_full")
  

perc_max_n <- max_n_data %>% 
  filter(site_full == "Percos") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

perc_max_n_full <- perc_max_n %>% 
  rbind(perc_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

perc_summary <- perc_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Percos")


#Refugio

refu_dates <- sampling_dates %>% 
  filter(site_full == "Refugio") %>% 
  select(site_full, date, bruv)

refu_sp <- species_list_site %>% 
  filter(site_full == "Refugio") %>% 
  merge(refu_dates, by="site_full")
  

refu_max_n <- max_n_data %>% 
  filter(site_full == "Refugio") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

refu_max_n_full <- refu_max_n %>% 
  rbind(refu_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

refu_summary <- refu_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Refugio")

#South Campus

soca_dates <- sampling_dates %>% 
  filter(site_full == "South Campus") %>% 
  select(site_full, date, bruv)

soca_sp <- species_list_site %>% 
  filter(site_full == "South Campus") %>% 
  merge(soca_dates, by="site_full")
  

soca_max_n <- max_n_data %>% 
  filter(site_full == "South Campus") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

soca_max_n_full <- soca_max_n %>% 
  rbind(soca_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

soca_summary <- soca_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "South Campus")

#Haskells

habe_dates <- sampling_dates %>% 
  filter(site_full == "Haskells") %>% 
  select(site_full, date, bruv)

habe_sp <- species_list_site %>% 
  filter(site_full == "Haskells") %>% 
  merge(habe_dates, by="site_full")
  

habe_max_n <- max_n_data %>% 
  filter(site_full == "Haskells") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

habe_max_n_full <- habe_max_n %>% 
  rbind(habe_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

habe_summary <- habe_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Haskells")

# Dume Cove

duco_dates <- sampling_dates %>% 
  filter(site_full == "Dume Cove") %>% 
  select(site_full, date, bruv)

duco_sp <- species_list_site %>% 
  filter(site_full == "Dume Cove") %>% 
  merge(duco_dates, by="site_full")
  

duco_max_n <- max_n_data %>% 
  filter(site_full == "Dume Cove") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

duco_max_n_full <- duco_max_n %>% 
  rbind(duco_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

duco_summary <- duco_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Dume Cove")

# Leo Carrillo 

leca_dates <- sampling_dates %>% 
  filter(site_full == "Leo Carrillo") %>% 
  select(site_full, date, bruv)

leca_sp <- species_list_site %>% 
  filter(site_full == "Leo Carrillo") %>% 
  merge(leca_dates, by="site_full")
  

leca_max_n <- max_n_data %>% 
  filter(site_full == "Leo Carrillo") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

leca_max_n_full <- leca_max_n %>% 
  rbind(leca_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

leca_summary <- leca_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Leo Carrillo")

# Sleepy Hollow

slho_dates <- sampling_dates %>% 
  filter(site_full == "Sleepy Hollow") %>% 
  select(site_full, date, bruv)

slho_sp <- species_list_site %>% 
  filter(site_full == "Sleepy Hollow") %>% 
  merge(slho_dates, by="site_full")
  

slho_max_n <- max_n_data %>% 
  filter(site_full == "Sleepy Hollow") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

slho_max_n_full <- slho_max_n %>% 
  rbind(slho_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

slho_summary <- slho_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Sleepy Hollow")

# Strands

stbe_dates <- sampling_dates %>% 
  filter(site_full == "Strands") %>% 
  select(site_full, date, bruv)

stbe_sp <- species_list_site %>% 
  filter(site_full == "Strands") %>% 
  merge(stbe_dates, by="site_full")
  

stbe_max_n <- max_n_data %>% 
  filter(site_full == "Strands") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

stbe_max_n_full <- stbe_max_n %>% 
  rbind(stbe_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

stbe_summary <- stbe_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Strands")

# Scripps

scri_dates <- sampling_dates %>% 
  filter(site_full == "Scripps") %>% 
  select(site_full, date, bruv)

scri_sp <- species_list_site %>% 
  filter(site_full == "Scripps") %>% 
  merge(scri_dates, by="site_full")
  

scri_max_n <- max_n_data %>% 
  filter(site_full == "Scripps") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

scri_max_n_full <- scri_max_n %>% 
  rbind(scri_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

scri_summary <- scri_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "Scripps")

# San Elijo

sael_dates <- sampling_dates %>% 
  filter(site_full == "San Elijo") %>% 
  select(site_full, date, bruv)

sael_sp <- species_list_site %>% 
  filter(site_full == "San Elijo") %>% 
  merge(sael_dates, by="site_full")
  

sael_max_n <- max_n_data %>% 
  filter(site_full == "San Elijo") %>% 
  filter(subclass == "Actinopterygii" | subclass == "Elasmobranchii") %>%
  select(site_full, date, geog, type, bruv, common, family_x, max_n)

sael_max_n_full <- sael_max_n %>% 
  rbind(sael_sp) %>% 
  group_by(date, bruv) %>% 
  arrange(-max_n) %>% 
  distinct(common, .keep_all = TRUE) %>% 
  arrange(date, bruv)

# Get summary stats on site

sael_summary <- sael_max_n_full %>% 
  group_by(common, family_x) %>% 
  summarize(mean_max_n = mean(max_n), 
            sd_max_n = sd(max_n),
            min = min(max_n), 
            max = max(max_n), 
            n = n()) %>% 
  mutate("Site" = "San Elijo")


# Merge into one table

mean_maxN_site_table <- perc_summary %>% 
  rbind(refu_summary) %>% 
  rbind(soca_summary) %>% 
  rbind(habe_summary) %>% 
  rbind(duco_summary) %>% 
  rbind(leca_summary) %>% 
  rbind(slho_summary) %>% 
  rbind(stbe_summary) %>% 
  rbind(scri_summary) %>% 
  rbind(sael_summary) %>% 
  relocate("Site", .before = "common")
  
```

***Table 3.** Summary statistics of average maxN of species at each site out of n deployments. This average includes maxN = 0 for deployments in which a species known to be present at the site is absent.*
```{r}
mean_maxN_site_table_wider <- mean_maxN_site_table %>%
  select("Site", "common", "family_x", "mean_max_n", "sd_max_n") %>% 
  pivot_wider(names_from = Site,
              values_from = c(mean_max_n, sd_max_n)
              ) %>% 
  clean_names() %>% 
  relocate(sd_max_n_percos, .after = mean_max_n_percos) %>% 
  relocate(sd_max_n_refugio, .after = mean_max_n_refugio) %>% 
  relocate(sd_max_n_south_campus, .after = mean_max_n_south_campus) %>%
  relocate(sd_max_n_haskells, .after = mean_max_n_haskells) %>% 
  relocate(sd_max_n_dume_cove, .after = mean_max_n_dume_cove) %>%
  relocate(sd_max_n_leo_carrillo, .after = mean_max_n_leo_carrillo) %>% 
  relocate(sd_max_n_sleepy_hollow, .after = mean_max_n_sleepy_hollow) %>% 
  relocate(sd_max_n_strands, .after = mean_max_n_strands) %>% 
  relocate(sd_max_n_scripps, .after = mean_max_n_scripps) %>% 
  relocate(sd_max_n_san_elijo, .after = mean_max_n_san_elijo) %>% 
  arrange(family_x) %>% 
  kable(digits=2, 
          col.names = c("Common name", "Family", "Percos Mean MaxN", "Percos SD", "Refugio Mean MaxN", "Refugio SD", "South Campus Mean MaxN", "South Campus SD", "Haskells Mean MaxN", "Haskells SD", "Dume Cove Mean MaxN", "Dume Cove SD", "Leo Carrillo Mean MaxN", "Leo Carrillo SD", "Sleepy Hollow Mean MaxN", "Sleepy Hollow SD", "Strands Mean MaxN", "Strands SD", "Scripps Mean MaxN", "Scripps SD", "San Elijo Mean MaxN", "San Elijo SD")) %>% 
  kable_styling()
mean_maxN_site_table_wider
```
**(a)**
```{r}
perc_refu <- perc_summary %>% 
  rbind(refu_summary)

ggplot(perc_refu, aes(x = common, y = mean_max_n)) +
  geom_bar(stat = "identity", 
           fill = "lightslategray") +
  coord_flip() +
  facet_wrap(~Site) +
  theme_minimal() +
  labs(x = "Common name", y = "Mean maxN")
```


**(b)**
```{r}
soca_habe <- soca_summary %>% 
  rbind(habe_summary)

ggplot(soca_habe, aes(x = common, y = mean_max_n)) +
  geom_bar(stat = "identity", 
           fill = "lightslategray") +
  coord_flip() +
  facet_wrap(~Site) +
  theme_minimal() +
  labs(x = "Common name", y = "Mean maxN")
```

**(c)**
```{r}
duco_leca <- duco_summary %>% 
  rbind(leca_summary)

ggplot(duco_leca, aes(x = common, y = mean_max_n)) +
  geom_bar(stat = "identity", 
           fill = "lightslategray") +
  coord_flip() +
  facet_wrap(~Site) +
  theme_minimal() +
  labs(x = "Common name", y = "Mean maxN")
```


**(d)**
```{r}
slho_stbe <- slho_summary %>% 
  rbind(stbe_summary)

ggplot(slho_stbe, aes(x = common, y = mean_max_n)) +
  geom_bar(stat = "identity", 
           fill = "lightslategray") +
  coord_flip() +
  facet_wrap(~Site) +
  theme_minimal() +
  labs(x = "Common name", y = "Mean maxN")
```


**(e)**
```{r}
scri_sael <- scri_summary %>% 
  rbind(sael_summary)

ggplot(scri_sael, aes(x = common, y = mean_max_n)) +
  geom_bar(stat = "identity", 
           fill = "lightslategray") +
  coord_flip() +
  facet_wrap(~Site) +
  theme_minimal() +
  labs(x = "Common name", y = "Mean maxN")
```



***Figure 7 (a-e).** Average MaxN of all species observed at each site for each site pair. Error bars were left off because of relatively large standard deviation (see Table 3). *

Pull species list from maxN data

```{r}
species_list_all_sites <- max_n_data %>% 
  filter(subclass %in% c("Actinopterygii", "Elasmobranchii")) %>% 
  select(site_full, type, geog, subclass, family_x, genus_x, species_x, sp_code, common) %>% 
  group_by(site_full) %>% 
  distinct(common, .keep_all = TRUE)

species_list_all <- max_n_data %>% 
  filter(subclass %in% c("Actinopterygii", "Elasmobranchii")) %>% 
  select(subclass, family_x, genus_x, species_x, sp_code, common) %>% 
  distinct(common, .keep_all = TRUE)
  
# Save to file

write.csv(species_list_all_sites, here::here("data", "species_list_sites.csv"))
write.csv(species_list_all, here::here("data", "species_list.csv"))
```

